\ttitle

### 2016-03-25 Chapters/Pre_Post_SIRS.tex
Body composition and tables
- Remove body comp vs alb/neut
- Remove some of the tables

There was no significant, persistent relationship between postoperative CRP and neutrophil count and preoperative neutrophil-lymphocyte ratio, SIMD score, body mass index, preoperative haemoglobin levels or the POSSUM Physiology score.

@@

The relationship between body composition and postoperative CRP, albumin and neutrophil count is shown in Tables \ref{table:sirs_bodycomp_crp}, \ref{table:sirs_bodycomp_alb} and \ref{table:sirs_bodycomp_neut} respectively.
Postoperative CRP and neutrophil count were not related to any of the components of body composition aside from a weak linear association between neutrophil count on POD 2 and visceral fat area (p=0.046).
However, lower preoperative skeletal muscle area was associated with lower postoperative serum albumin on days 1 to 5 (all p$<$0.05).

@@

\input{Tables/sirs_albumin}
\input{Tables/sirs_alb_pvalues}

\input{Tables/sirs_neut}
\input{Tables/sirs_neut_pvalues}

>>>>

There was no significant, persistent relationship between postoperative CRP and preoperative SIMD score, body mass index, preoperative haemoglobin levels or the POSSUM Physiology score.

@@

The relationship between body composition and postoperative CRP is shown in Table \ref{table:sirs_bodycomp_crp}.
Postoperative CRP was not related to any of the components of body composition.

@@
